\textbf{Appendix}\\ Step by Step: Using Integrated Step Selection Analysis to Simulate Wild Dog Dispersal and Assess Landscape Connectivity

### 2021-09-25 Chapter_1/04_Manuscript/Manuscript.tex
Various updates

\subsection{Betweenness}
The betweenness map (\Cref{Betweenness}) revealed distinct dispersal corridors
that run within the KAZA-TFCA . Again, the region in northern Botswana emerged
as wild dog dispersal hub that connected more remote regions in the study area.
Towards east, the extension of this corridor ran through Chobe National Park
into Hwange National Park. From there, a further extension connected to
Matusadona National Park in Zimbabwe. Northwest of the Linyanty ecosystem, a
major corridor expanded into Angola, where it splitted and finally traversed
over a long stretch of unprotected area into Zambia's Kafue National Park.
Several additional corridors with lower betweenness scores emerged, yet most of
them ran within the KAZA-TFCA boundaries (median betweenness inside KAZA-TFCA =
6947\(k\), IQR = 54311\(k\), Figure S6b). In general, there were few corridors
that directly linked the peripheral regions of the KAZA-TFCA and passed through
unprotected areas outside the KAZA-TFCA (mean betweenness outside KAZA =
2685\(k\), IQR = 9891\(k\), Figure S6b). Compared to the heatmap, the
betweenness map facilitated the identification of dispersal corridors between
habitat patches.

@@

\subsection{Inter-Patch Connectivity}
The map of inter-patch connectivity showed that the relative frequency at which
simulated dispersers moved from one national park to another varied, as did the
average dispersal duration required to make these connections
(\Cref{InterpatchConnectivity}). Overall, interpatch connectivity between
national parks in Angola, Namibia, and Botswana appeared to be high (mean
relative frequency = +- ) with short dispersal durations (mean duration = +-)

>>>>

\subsection{Betweenness}
The betweenness map (\Cref{Betweenness}) revealed distinct dispersal corridors
that run within the KAZA-TFCA. Again, the region in northern Botswana emerged
as wild dog dispersal hub that connected more remote regions in the study area.
Towards east, the extension of this corridor ran through Chobe National Park
into Hwange National Park. From there, a further extension connected to
Matusadona National Park in Zimbabwe. Northwest of the Linyanty ecosystem, a
major corridor expanded into Angola, where it splitted and finally traversed
over a long stretch of unprotected area into Zambia's Kafue National Park.
Several additional corridors with lower betweenness scores emerged, yet most of
them ran within the KAZA-TFCA boundaries (median betweenness inside KAZA-TFCA =
6947\(k\), IQR = 54311\(k\), Figure S6b). In general, there were few corridors
that directly linked the peripheral regions of the KAZA-TFCA and passed through
unprotected areas outside the KAZA-TFCA (mean betweenness outside KAZA-TFCA =
2685\(k\), IQR = 9891\(k\), Figure S6b). Compared to the heatmap, the
betweenness map facilitated the identification of dispersal corridors between
habitat patches.

@@

\subsection{Inter-Patch Connectivity}
The map of inter-patch connectivity showed that the relative frequency at which
simulated dispersers moved from one national park to another varied, as did the
average dispersal duration required to make these connections
(\Cref{InterpatchConnectivity}).

Overall, interpatch connectivity between national parks in Angola, Namibia,
Botswana, and Zimbabwe appeared to be high with only short required dispersal
durations. For example, xx\% of simulated individuals departing from a national
park in xx managed to move into a national park in xx, with average dispersal
durations of xx\% steps. Conversely, we found that connectivity from and into
national parks in Zambia were limited. Only xx\% of the dispersers leaving from
Zambia managed to move into a national park in another country and for those
connections xx steps were required on average. In some cases, we also detected
imbalances between the number of ingoing and outgoing links. Make an example...

 suggesting the presence of source-sink dynamics that occure due to asymmetric behavior depending on the direction in which a certain dispersal route is taken.

### 2021-09-25 Chapter_1/04_Manuscript/Manuscript_Support.tex
Various updates

%------------------------------------------------------------------------------
%	Appendix S9: Evolution of Betweenness Maps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=10mm,footskip=0pt}
\section{Betweenness Maps in Relation to Number of Simulated Steps}
\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = 0.86\textwidth]{99_BetweennessIndividual.png}
  \caption{Maps of betweenness scores produced when considering (a) 125, (b)
   500, (c) and 2000 simulated steps, respectively. A high betweenness score
   indicates that the respective area has a high importance for linking other
   regions in the study area.}
  \label{Betweenness}
 \end{center}
\end{figure}
\restoregeometry

%------------------------------------------------------------------------------
%	Appendix S10: Map Comparison
%------------------------------------------------------------------------------
\newpage
\section{Comparison of Values Inside and Outside of KAZA-TFCA}
\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = \textwidth]{99_MapComparison.png}
  \caption{Comparison of values from the heatmap and betweenness map inside
  (blue) and outside (orange) the KAZA-TFCA borders.}
  \label{MapComparison}
 \end{center}
\end{figure}

>>>>

%------------------------------------------------------------------------------
%	Appendix S9: Evolution of Betweenness Maps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=10mm,footskip=0pt}
\section{Betweenness Maps in Relation to Number of Simulated Steps}
\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = 0.86\textwidth]{99_BetweennessIndividual.png}
  \caption{Maps of betweenness scores produced when considering (a) 125, (b)
   500, (c) and 2000 simulated steps, respectively. A high betweenness score
   indicates that the respective area has a high importance for linking other
   regions in the study area.}
  \label{Betweenness}
 \end{center}
\end{figure}
\restoregeometry
%------------------------------------------------------------------------------
%	Appendix S11: Areas Reached
%------------------------------------------------------------------------------
\newpage
\section{Dispersal into other National Parks}
\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = \textwidth]{99_AreasReached.png}
  \caption{Relative number of simulated dispersal trajectories that successfully
  moved from one national park into another that is at least as far away as
  indicated on the x-axis. Percentages are given in relation to the number of
  simulated individuals from the national parks in the respective countries. For
  example, over 85\% of all individuals originating from a national park in
  Angola moved from their natal national park into another one. However, the
  percentage gradually decreases as only national parks at higher euclidean
  distances are considered.}
  \label{AreasReached}
 \end{center}
\end{figure}

%------------------------------------------------------------------------------
%	Appendix S11: Map Comparison
%------------------------------------------------------------------------------
\newpage
\section{Comparison of Traversal Frequencies and Betweenness Scores Inside and Outside KAZA-TFCA}
\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = \textwidth]{99_MapComparison.png}
  \caption{Comparison of values from the heatmap and betweenness map inside
  (blue) and outside (orange) the KAZA-TFCA borders.}
  \label{MapComparison}
 \end{center}
\end{figure}
